A data-intensive assessment of the species-abundance distribution.

### 2015-03-28 defense_pres.tex
Changes something minor.
Adds some additional graphs, section on signal and noise.

\begin{frame}[t]
\titlepage
\end{frame}

@@

@@

\section{Data}
\subsection{Introduction to Ecoinformatics}
\begin{frame}[t]
\frametitle{The Rules of Ecoinformatics}
\begin{Large}
Garbage in, garbage out.\\
\end{Large}
\begin{itemize}
\item All data are good, not all data are appropriate.
\item Fit the data to the question.
\end{itemize}
\end{frame}

\subsection{Current Data}
\begin{frame}[t]
\frametitle{Data}
\vspace{-7pt}
\includegraphics[scale=.55]{./sad-data/chapter3/presentation_map.png}
\end{frame}

@@

\subsection{Compiled Data}
\subsubsection{Data Collection}
\begin{frame}[shrink=30]
\frametitle{Data}
\begin{table}
\begin{tabular}{l|l} 
 Variable name & Variable definitions\\ 
\hline
 Class & Taxonomic class of species \\
 Family & Taxonomic family of species \\
 Genus & Taxonomic genus of species\\
 Species & Specific epithet of species  \\
 Relative\_abundance & Relative abundance of species \\
 Abundance & Abundance of species \\
 Collection\_Year & Start of collecting \\
 End\_Collection & End of collecting \\
 Site\_Name & Name/description of site \\
 Biogeographic\_region & Biogeographic region \\
 Site\_notes & Additional site information \\ 
\end{tabular}
\caption{List of variables collected.}
\end{table}
\end{frame}

\subsubsection{Data Summary}
\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
\end{frame}

\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.5]{./sad-data/dissertation/bioregions.png}
\end{frame}

@@

\subsection{Results}
\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale=.5]{./sad-data/dissertation/AICc_weights.png}
\end{frame}

@@

>>>>

\section{Title}
\begin{frame}[t]
\titlepage
\end{frame}

@@

\subsection{Signal and Noise}
\begin{frame}[t]
\frametitle{Signal \& Noise}
\begin{center}
\includegraphics[scale=.05]{../Miscellaneous/Pictures/Maps/TheMapsCoarse.png}
\end{center}
\end{frame}

\begin{frame}[t]
\frametitle{Signal \& Noise}
\begin{center}
\includegraphics[scale=.05]{../Miscellaneous/Pictures/Maps/TheMapsMiddle.png}
\end{center}
\end{frame}

\begin{frame}[t]
\frametitle{Signal \& Noise}
\begin{center}
\includegraphics[scale=.2]{../Miscellaneous/Pictures/Maps/TheMaps.png}
\end{center}
\end{frame}

@@

\subsection{Introduction to Ecoinformatics}
\begin{frame}[t]
\frametitle{The Rules of Ecoinformatics}
\begin{Large}
Garbage in, garbage out.\\
\end{Large}
\begin{itemize}
\item All data are good, not all data are appropriate.
\item Fit the data to the question.
\end{itemize}
\end{frame}

\section{Data}
\subsection{Current Data}
\begin{frame}[t]
\frametitle{Data}
\vspace{-7pt}
\includegraphics[scale=.55]{./sad-data/chapter3/presentation_map.png}
\end{frame}

@@

\subsection{Compiled Data}
\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.35]{../Miscellaneous/Pictures/Phd/CompiledData.png}
\end{frame}

\subsubsection{Data Collection}
\begin{frame}[shrink=30]
\frametitle{Data}
\begin{table}
\begin{tabular}{l|l} 
 Variable name & Variable definitions\\ 
\hline
 Class & Taxonomic class of species \\
 Family & Taxonomic family of species \\
 Genus & Taxonomic genus of species\\
 Species & Specific epithet of species  \\
 Relative\_abundance & Relative abundance of species \\
 Abundance & Abundance of species \\
 Collection\_Year & Start of collecting \\
 End\_Collection & End of collecting \\
 Site\_Name & Name/description of site \\
 Biogeographic\_region & Biogeographic region \\
 Site\_notes & Additional site information \\ 
\end{tabular}
\caption{List of variables collected.}
\end{table}
\end{frame}

\subsubsection{Data Summary}
\begin{frame}{}
\frametitle{Data}
\includegraphics[scale=.5]{./sad-data/dissertation/bioregions.png}
\end{frame}

@@

\subsection{Results}
\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale=.5]{./sad-data/dissertation/total_wins.png}
\end{frame}

\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale=.40]{./sad-data/dissertation/wins_by_dataset.png}
\end{frame}

\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale=.5]{./sad-data/dissertation/AICc_weights.png}
\end{frame}

@@

\section{Finis}
\begin{frame}[t]
\frametitle{Questions?}
\begin{center}
\includegraphics[scale=.2]{../Miscellaneous/Pictures/Maps/TheMaps.png}
\end{center}
\end{frame}
